\textls[-0]{\thetitle}

### 2022-11-11 agda-files.tex
add refs
small edits

In the ``Other supplemental material'' section of the submission, we
include the complete formalization of \TT.
It consists of four files in Agda syntax.
%

@@

This file defines the standard model from which
\cref{thm:consistency} (consistency) follows.

@@

This file defines the logical-relations model from which
\cref{thm:canonicity} (canonicity) follows.

>>>>

In the ``Other supplemental material'' section of the submission, we
include the definitive, complete formalization of \TT.
It consists of four files in Agda syntax.
%

@@

This file defines the standard model from which
\cref{thm:consistency} (consistency) follows.
%
The construction largely follows the standard model of
\cite{altkap2016,kaposi2017type,kaposi2019gluing}.

@@

This file defines the logical-relations model from which
\cref{thm:canonicity} (canonicity) follows.
%
The construction largely follows that in
\cite{coquand2018canonicity,sterling2019algebraic}.
